Title

### 2012-01-23 inc/laser/laser.tex

% insert figure 1 here

>>>>

\begin{figure}
  \subfloat[][]{
    \label{fig:crystal_geo}
    \input{crystal_geo}
  }
  \caption{
\subref{fig:crystal_geo} Top view of the 3x3x10mm AR coated Yb:KGW laser crystal showing the crystal cut, the direction of propagation of p-polarized laser radiation at 1040nm, and the $x$ (tangential) and $y$ (saggital) directions (in blue) employed in the thermal analysis;
(b) Calculated reflectivity of the 193nm \ce{SiO2} AR coating as a function of incidence angle for $p$-polarized 1040nm laser radiation (solid line) and $s$-polarized 980nm pump radiation (dashed line).
}
\end{figure}
